Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
more stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58611 72bbbca6-d526-0410-a7d9-f06f51895060

For the normalised version, we changed only morphology and vocabulary. On the lexical level, the word \emph{seiska} `number 7' is colloquial style, and in the standard translation it is replaced by the ordinal \emph{seitsem\"{a}s} `seventh'.  Other changes in the normalised version are common morphological or phonological, phenomena, such as reducing the diphthong in \emph{vain} $\rightarrow$ \emph{vaan} or shortening in  \emph{ett\"{a}} $\rightarrow$ \emph{et}. The original sentence and the normalised translation are shown below, aligned word by word.

@@

% expand test corpus -- up to 10,000 words
% add other colloquial genres
% apply to other NLP tasks
% weight rules 
%

@@

As for the methods, we would like to follow \newcite{scannell2014} in incorporating
`translation' probabilities into our normalisation model. Our current model relies 
exclusively on the target-language model probability, however some rules may be more
reliable or probable than others.

>>>>

For the normalised version,\footnote{The normalised version is converted orthographically and lexically, but not syntactically or stylistically.} we changed only morphology and vocabulary. On the lexical level, the word \emph{seiska} `number 7' is colloquial style, and in the standard translation it is replaced by the ordinal \emph{seitsem\"{a}s} `seventh'.  Other changes in the normalised version are common morphological or phonological, phenomena, such as reducing the diphthong in \emph{vain} $\rightarrow$ \emph{vaan} or shortening in  \emph{ett\"{a}} $\rightarrow$ \emph{et}. The original sentence and the normalised translation are shown below, aligned word by word.

@@

@@

As for the methods, we would like to follow \newcite{scannell2014} in incorporating
`translation' probabilities into our unsupervised normalisation model. Our current model relies 
exclusively on the target-language model probability, however some rules may be more
reliable or probable than others.
